%# -*- coding: utf-8-unix -*-
%%==================================================
%% pub.tex for SJTUThesis
%% Encoding: UTF-8
%%==================================================

\begin{publications}{99}
\item\textsc{Noblesse F, He J, Zhu Y, et al}. {
  Why can ship wakes appear narrower than Kelvin's angle?}[J]. 
  European Journal of Mechanics-B/Fluids, 2014, 46: 164-171.
\item\textsc{He J, Zhang C, Zhu Y, et al}. {
  Comparison of three simple models of Kelvin's ship wake}[J]. 
  European Journal of Mechanics-B/Fluids, 2015, 49: 12-19.
\item\textsc{Zhang C, He J, Zhu Y, et al}. {
  Interference effects on the Kelvin wake of a monohull ship represented via a continuous distribution of sources}[J]. 
  European Journal of Mechanics-B/Fluids, 2015, 51: 27-36.
\item\textsc{He J, Zhang C, Zhu Y, et al}. {
    Interference effects on the Kelvin wake of a catamaran 
  represented via a hull-surface distribution of sources}[J].
  European Journal of Mechanics-B/Fluids, 2016, 56: 1-12.
\item\textsc{He J, Zhang C, Noblesse F, et al}. {
  A Family of Ship Hulls for Drag-Optimization Studies}[C]
  //The Twenty-fourth International Ocean and Polar Engineering Conference. 
  International Society of Offshore and Polar Engineers, 2014.
\item\textsc{He J, Zhang C, Zhu Y, et al}. {
    Analysis of Wave-Interference Effects on the Kelvin Wakes of
  Monohull Ships and Catamarans}[C]
    //Proceedings of the 9th International Workshop on Ship and
    Marine Hydrodynamics, 2015.
\end{publications}
